Government websites as data: A methodological pipeline for collection, processing, and text analysis

### 2017-12-19 paper/presentation/Markus_SPSA_2018_Presentation.tex
updates to the presentation

\documentclass[12pt]{beamer}
\setbeamertemplate{navigation symbols}{}
%\usepackage[latin1]{inputenc}
\usepackage{pgfplots}
\usepackage{adjustbox}
\usepackage{graphicx}
%\usepackage{draftwatermark}
\usepackage{tikz}
\usepackage{subfigure}
%\usetheme{Amsterdam}
\usecolortheme{default}
\title[]{The effects of transitions of power on the contents of
	municipal government websites}
\author{Markus Neumann \\ Fridolin Linder \\ Bruce Desmarais}
\institute{The Pennsylvania State University}
\date{January 6, 2018}

\makeatletter
\defbeamertemplate*{footline}{myminiframes theme}
{%
	\begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
	\end{beamercolorbox}
	\hbox{%
		\begin{beamercolorbox}[wd=.1\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}%\insertframenumber/\inserttotalframenumber}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.75\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			\leavevmode{\usebeamerfont{title in head/foot}\insertshorttitle}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.15\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}%\insertshortauthor}
		\end{beamercolorbox}%
	}%
	\begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
	\end{beamercolorbox}
}
\makeatother

@@

\begin{frame}{Government Websites}
\linespread{1.5}
{\large
	\begin{itemize}
		\item Most local (i.e. mayoral) elections are non-partisan
		\item Few states have exclusively partisan local elections
		\item Data for these elections can be difficult to find
		\item We selected Indiana and Louisiana
	\end{itemize}

@@

\begin{frame}{Maps}
\begin{figure}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
\end{figure}
\end{frame}

\begin{frame}{The Pipeline}
	\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Scraping URLs
		\item Browser automation to verify URLs
		\item Download sites with wget
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item Duplicate content removal
		\item Spellchecking
		\item Lemmatization
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		\item Hierarchical clustering
		\item Fightin' Words
		\item Topic models
		\begin{itemize}
			\item LDA
			\item STM
		\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

\begin{frame}{The Pipeline}
\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Scraping URLs
		\item Browser automation to verify URLs
		\item Download sites with wget
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item \textbf{Duplicate content removal}
		\item Spellchecking
		\item Lemmatization
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		\item Hierarchical clustering
		\item Fightin' Words
		\item Topic models
		\begin{itemize}
			\item LDA
			\item STM
		\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

@@

\begin{frame}{Duplicate Content Removal}
\includegraphics[width = \linewidth]{arcadia_water.png}
\end{frame}

\begin{frame}{Duplicate Content Removal}
\includegraphics[width = \linewidth]{duplicateLines.png}
\end{frame}

\begin{frame}{Duplicate Content Removal}
	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
\end{frame}

\begin{frame}{Duplicate Content Removal}
\begin{itemize}
	\item Within each city, there is a lot of shared text
	\begin{itemize}
		\item Boilerplate
		\item Website elements
	\end{itemize}
	\item If not removed, the text clusters into cities
\end{itemize}
\begin{itemize}
	\item Solution: Compare each line in each document to every other line in every document of that city
	\item Count duplicates
	\item Remove a line if it is duplicated within a city above some threshold
	\item Hash tables for computational efficiency
\end{itemize}
\end{frame}

\begin{frame}{The Pipeline}
\textbf{Data Collection} \hspace{2mm} --> \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} --> \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Scraping URLs
		\item Browser automation to verify URLs
		\item Download sites with wget
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item Duplicate content removal
		\item Spellchecking
		\item Lemmatization
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		\item Hierarchical clustering
		\item Fightin' Words
		\item Topic models
		\begin{itemize}
			\item LDA
			\item STM
		\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

@@

\section{Analysis}
\begin{frame}{Hierarchical Clustering}
\centering
\includegraphics[height=\textheight]{../figures/heatmap_hclust_40.png}
\end{frame}

\begin{frame}{Fightin' Words}
\begin{figure}
	\hfill
	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsIN.png}}
	\hfill
	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsLA.png}}
\end{figure}
\end{frame}

\begin{frame}{Latent Dirichlet Allocation}

\input{partisanTopWords.tex}

\end{frame}

@@

\section{Conclusion}
\begin{frame}{Conclusion}
%\linespread{1.5}
\large
\begin{itemize}
	\item Hierarchical clustering only creates 'topics' if content is VERY similar
	\item Fightin words is extremely effective at forcing the text into two categories, but also somewhat limited
	\item LDA is sensitive to preprocessing, but the most flexible
	\item STM works too, but also very sensitive to duplicate content
	\vspace{5mm}
	\item Democrats focus on raising and spending money, Republicans on infrastructure and basic utilities
\end{itemize}
\end{frame}

>>>>

\documentclass[12pt]{beamer}
\setbeamertemplate{navigation symbols}{}
%\usepackage[latin1]{inputenc}
\usepackage{pgfplots}
\usepackage{adjustbox}
\usepackage{graphicx}
%\usepackage{draftwatermark}
\usepackage{tikz}
\usepackage{colortbl}
\usepackage{subfigure}
%\usetheme{Amsterdam}
\usecolortheme{default}
\title[]{Government websites as data: A methodological pipeline for
collection, processing, and text analysis}
\author{Markus Neumann \\ Fridolin Linder \\ Bruce Desmarais}
\institute{The Pennsylvania State University}
\date{January 6, 2018}

\makeatletter
\defbeamertemplate*{footline}{myminiframes theme}
{%
	\begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
	\end{beamercolorbox}
	\hbox{%
		\begin{beamercolorbox}[wd=.1\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}{\insertframenumber}%/\inserttotalframenumber}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.75\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			\leavevmode{\usebeamerfont{title in head/foot}\insertshorttitle}%
		\end{beamercolorbox}%
		\begin{beamercolorbox}[wd=.15\paperwidth,ht=2.5ex,dp=1.125ex,%
			leftskip=.3cm,rightskip=.3cm plus1fil,center]{title in head/foot}%
			{\usebeamerfont{author in head/foot}\usebeamercolor[fg]{author in head/foot}}%\insertshortauthor}
		\end{beamercolorbox}%
	}%
	\begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
	\end{beamercolorbox}
}
\makeatother

@@

\begin{frame}{Example Website}
	\includegraphics[width = \linewidth]{arcadia_water.png}
\end{frame}

\begin{frame}{Local Government Websites}
\linespread{1.5}
{\large
	\begin{itemize}
		\item Most local (i.e. mayoral) elections are non-partisan
		\item Few states have exclusively partisan local elections
		\item Data for these elections can be difficult to find
		\item We selected Indiana and Louisiana
	\end{itemize}

@@

\begin{frame}{Data Overview}
\begin{figure}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/indiana_map.pdf}}
	\hfill
	\subfigure{\includegraphics[width=5cm, height = .7\textheight]{../figures/louisiana_map.pdf}}
\end{figure}
\end{frame}

\begin{frame}{The Pipeline}
	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
\begin{columns}
	\column{0.33\textwidth}
	%Data Collection
	\vspace{5mm}
	\begin{itemize}
		\item Identify URLs
		\item Verify URLs (browser automation)
		\item Download websites
		\item Determine file type
		\item Convert to txt
	\end{itemize}		
	\column{0.33\textwidth}
	%Preprocessing
	\vspace{5mm}
	\begin{itemize}
		\item Remove punctuation, dates, etc.
		\item To lowercase
		\item Boilerplate removal
		\item Spellchecking
		\item Lemmatization \\ (city \& cities = city)
	\end{itemize}
	\column{0.33\textwidth}
	%Analysis
	\vspace{5mm}
	\begin{itemize}
		%\item Hierarchical clustering
		\item Fightin' Words
		\item Structural topic model
		%\begin{itemize}
		%	\item LDA
		%	\item STM
		%\end{itemize}
	\end{itemize}
\end{columns}
\end{frame}

\begin{frame}{The Pipeline}
	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
	\begin{columns}
		\column{0.33\textwidth}
		%Data Collection
		\vspace{5mm}
		\begin{itemize}
			\item Identify URLs
			\item Verify URLs (browser automation)
			\item Download websites
			\item Determine file type
			\item Convert to txt
		\end{itemize}		
		\column{0.33\textwidth}
		%Preprocessing
		\vspace{5mm}
		\begin{itemize}
			\item Remove punctuation, dates, etc.
			\item To lowercase
			\item \textbf{Boilerplate removal}
			\item Spellchecking
			\item Lemmatization \\ (city \& cities = city)
		\end{itemize}
		\column{0.33\textwidth}
		%Analysis
		\vspace{5mm}
		\begin{itemize}
			%\item Hierarchical clustering
			\item Fightin' Words
			\item Structural topic model
			%\begin{itemize}
			%	\item LDA
			%	\item STM
			%\end{itemize}
		\end{itemize}
	\end{columns}
\end{frame}

@@

\begin{frame}{Boilerplate Removal}
\includegraphics[width = \linewidth]{arcadia_water.png}
\end{frame}

\begin{frame}{Boilerplate Removal}
\includegraphics[width = \linewidth]{duplicateLines.png}
\end{frame}

\begin{frame}{Boilerplate Removal}
	\includegraphics[width = \linewidth]{duplicateLineRemoval.png}
\end{frame}

\begin{frame}{Boilerplate Removal}
\begin{itemize}
	\item Within each city, there is a lot of shared text
	\item If not removed, the text clusters into cities
\end{itemize}
\begin{itemize}
	\item Solution: Compare each line in each document to every other line in every document of that city
	\item Count duplicates
	\item Remove a line if it is duplicated within a city above some threshold
	\item Fast \& efficient implementation
\end{itemize}
\end{frame}

\begin{frame}{The Pipeline}
	\textbf{Data Collection} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Preprocessing} \hspace{2mm} $\rightarrow$ \hspace{2mm} \textbf{Analysis}
	\begin{columns}
		\column{0.33\textwidth}
		%Data Collection
		\vspace{5mm}
		\begin{itemize}
			\item Identify URLs
			\item Verify URLs (browser automation)
			\item Download websites
			\item Determine file type
			\item Convert to txt
		\end{itemize}		
		\column{0.33\textwidth}
		%Preprocessing
		\vspace{5mm}
		\begin{itemize}
			\item Remove punctuation, dates, etc.
			\item To lowercase
			\item Boilerplate removal
			\item Spellchecking
			\item Lemmatization \\ (city \& cities = city)
		\end{itemize}
		\column{0.33\textwidth}
		%Analysis
		\vspace{5mm}
		\begin{itemize}
			%\item Hierarchical clustering
			\item Fightin' Words
			\item Structural topic model
			%\begin{itemize}
			%	\item LDA
			%	\item STM
			%\end{itemize}
		\end{itemize}
	\end{columns}
\end{frame}

@@

\section{Analysis}
%\begin{frame}{Hierarchical Clustering}
%\centering
%\includegraphics[height=\textheight]{../figures/heatmap_hclust_40.png}
%\end{frame}

%\begin{frame}{Fightin' Words}
%\begin{figure}
%	\hfill
%	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsIN.png}}
%	\hfill
%	\subfigure{\includegraphics[width=5cm]{../figures/fightinWordsLA.png}}
%\end{figure}
%\end{frame}

\begin{frame}{Fightin' Words}
	\input{fightinwordsIN.tex} %../tables/stmTopWordsINDem.tex
\end{frame}

%\begin{frame}{Latent Dirichlet Allocation}
%\input{partisanTopWords.tex}
%\end{frame}

@@

\section{Conclusion}
\begin{frame}{Conclusion}
\linespread{1.5}
\large
\begin{itemize}
	%\item Hierarchical clustering only creates 'topics' if content is VERY similar
	%\item Fightin words is extremely effective at forcing the text into two categories, but also somewhat limited
	%\item LDA is sensitive to preprocessing, but the most flexible
	%\item STM works too, but also very sensitive to duplicate content
	\item Manual vs. automatic analysis of government websites
	\item Our pipeline facilities scalable comparative analysis

	\vspace{5mm}
	\item Partisanship affects website content:
	\item Democrats focus on raising and spending money
	\item Republicans focus on infrastructure and utilities
\end{itemize}
\end{frame}

### 2017-12-19 paper/presentation/stmTopWordsINDem.tex
updates to the presentation

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
-0.026 & -0.019 & -0.018 & -0.018 & -0.018 & -0.013 \\ 
  \hline
fort & propos & said & prosecutor & digest & fund \\ 
  citi & author & ask & charg & introduc & grant \\ 
  ordin & district & state & feloni & author & budget \\ 
  approv & street & will & counti & counti & counti \\ 
  purchas & public & chair & case & appoint & state \\ 
  depart & control & propos & crime & board & feder \\ 
  properti & amend & year & crimin & approv & depart \\ 
  will & intersect & move & offic & district & appropri \\ 
  resolut & counti & need & victim & fund & increas  \\ 
  contract & committe & council & sentenc & street & agenc \\ 
   \hline
\end{tabular}
%\caption{Top Democratic topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINDem}
\end{table}

>>>>

%\usepackage[table]{xcolor}
% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
-0.026 & -0.019 & -0.018 & -0.018 & -0.018 & -0.013 \\ 
  \hline
fort & propos & said & prosecutor & digest & \cellcolor{blue!25} fund \\ 
  citi & author & ask & charg & introduc & \cellcolor{blue!25} grant \\ 
  ordin & district & state & feloni & author & \cellcolor{blue!25} budget \\ 
  approv & street & will & counti & counti & counti \\ 
  \cellcolor{blue!25} purchas & public & chair & case & appoint & state \\ 
  depart & control & propos & crime & board & feder \\ 
  properti & amend & year & crimin & approv & depart \\ 
  will & intersect & move & offic & district & appropri \\ 
  resolut & counti & need & victim & \cellcolor{blue!25} fund & increas  \\ 
  contract & committe & council & sentenc & street & agenc \\ 
   \hline
\end{tabular}
%\caption{Top Democratic topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINDem}
\end{table}

### 2017-12-19 paper/presentation/stmTopWordsINRep.tex
updates to the presentation

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
0.024 & 0.019 & 0.019 & 0.016 & 0.016 & 0.016 \\ 
  \hline
motion & plan & inc & request & council & traffic \\ 
  second & zone & electr & board & citi & amp \\ 
  made & applic & build & member & ordin & vehicl \\ 
  approv & properti & construct & servic & common & stop \\ 
  mayor & approv & home & street & councilor & sign \\ 
  present & sign & street & approv & amend & road \\ 
  state & site & meridian & purchas & resolut & block \\ 
  will & locat & servic & citi & adopt & signal \\ 
  citi & commiss & west & move & wherea & street \\ 
  council & file & main & good & approv & driver \\ 
   \hline
\end{tabular}
%\caption{Top Republican topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINRep}
\end{table}

>>>>

% latex table generated in R 3.4.2 by xtable 1.8-2 package
% Mon Nov 13 15:36:58 2017
\begin{table}[ht]
\centering
\begin{tabular}{llllll}
  \hline
0.024 & 0.019 & 0.019 & 0.016 & 0.016 & 0.016 \\ 
  \hline
motion & plan & inc & request & council & \cellcolor{red!25} traffic \\ 
  second & \cellcolor{red!25} zone & electr & board & citi & amp \\ 
  made & applic & build & member & ordin & vehicl \\ 
  approv & \cellcolor{red!25} properti & construct & servic & common & stop \\ 
  mayor & approv & home & \cellcolor{red!25} street & councilor & sign \\ 
  present & sign & street & approv & amend & \cellcolor{red!25} road \\ 
  state & \cellcolor{red!25} site & meridian & purchas & resolut & block \\ 
  will & locat & servic & citi & adopt & signal \\ 
  citi & commiss & west & move & wherea & \cellcolor{red!25} street \\ 
  council & file & main & good & approv & driver \\ 
   \hline
\end{tabular}
%\caption{Top Republican topics and words (Indiana), according to STM. 
%The words are the top words for the most Democratic/Republican topic, determined
%by the size (and significance) of the coefficient (see table header) of the party covariate.} 
\label{tabSTMINRep}
\end{table}
